Crystal as a thermodynamic computer

### 2024-09-16 paper/main.tex
enlarge the circles and texts in the inset picture of Fig.1

%Shape: Circle [id:dp3980815479811872] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (491,154.1) .. controls (491,151.61) and (493.01,149.6) .. (495.5,149.6) .. controls (497.99,149.6) and (500,151.61) .. (500,154.1) .. controls (500,156.59) and (497.99,158.6) .. (495.5,158.6) .. controls (493.01,158.6) and (491,156.59) .. (491,154.1) -- cycle ;
%Shape: Circle [id:dp8208493476316323] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (491,191.1) .. controls (491,188.61) and (493.01,186.6) .. (495.5,186.6) .. controls (497.99,186.6) and (500,188.61) .. (500,191.1) .. controls (500,193.59) and (497.99,195.6) .. (495.5,195.6) .. controls (493.01,195.6) and (491,193.59) .. (491,191.1) -- cycle ;

@@

\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (478.67,172.6) .. controls (478.67,170.11) and (480.68,168.1) .. (483.17,168.1) .. controls (485.65,168.1) and (487.67,170.11) .. (487.67,172.6) .. controls (487.67,175.09) and (485.65,177.1) .. (483.17,177.1) .. controls (480.68,177.1) and (478.67,175.09) .. (478.67,172.6) -- cycle ;
%Shape: Circle [id:dp967421569400009] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (503.4,172.6) .. controls (503.4,170.11) and (505.41,168.1) .. (507.9,168.1) .. controls (510.39,168.1) and (512.4,170.11) .. (512.4,172.6) .. controls (512.4,175.09) and (510.39,177.1) .. (507.9,177.1) .. controls (505.41,177.1) and (503.4,175.09) .. (503.4,172.6) -- cycle ;
%Shape: Circle [id:dp938870324276512] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (524.7,172.5) .. controls (524.7,170.01) and (526.71,168) .. (529.2,168) .. controls (531.69,168) and (533.7,170.01) .. (533.7,172.5) .. controls (533.7,174.99) and (531.69,177) .. (529.2,177) .. controls (526.71,177) and (524.7,174.99) .. (524.7,172.5) -- cycle ;

@@

\draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (475.6,155.04) .. controls (475.6,148.59) and (480.83,143.36) .. (487.28,143.36) -- (525.12,143.36) .. controls (531.57,143.36) and (536.8,148.59) .. (536.8,155.04) -- (536.8,190.08) .. controls (536.8,196.53) and (531.57,201.76) .. (525.12,201.76) -- (487.28,201.76) .. controls (480.83,201.76) and (475.6,196.53) .. (475.6,190.08) -- cycle ;

@@

\draw    (491,154.1) -- (469.8,154.1) ;

@@

\draw    (478.67,172.47) -- (469.8,172.5) ;

@@

\draw    (491,191.1) -- (469.8,191.1) ;

@@

\draw    (483.17,172.6) -- (495.5,154.1) ;

@@

\draw    (483.17,172.6) -- (495.5,191.1) ;

@@

\draw    (495.5,154.1) -- (507.9,172.6) ;

@@

\draw    (495.5,191.1) -- (507.9,172.6) ;

@@

\draw    (483.17,172.6) -- (507.9,172.6) ;

@@

\draw    (495.5,191.1) -- (495.5,154.1) ;

@@

\draw    (495.5,191.1) .. controls (509.12,191.04) and (521.92,189.04) .. (529.2,172.5) ;

@@

\draw    (495.5,154.1) .. controls (511.92,153.84) and (524.32,158.24) .. (529.2,172.5) ;

@@

\draw    (529.2,172.5) .. controls (514.32,159.44) and (495.92,161.04) .. (483.17,172.6) ;

@@

\draw    (529.2,172.5) .. controls (523.52,180.64) and (511.92,179.84) .. (507.9,172.6) ;

@@

\draw    (533.7,172.5) -- (541.8,172.5) ;
%Shape: Circle [id:dp28592847133985866] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (478.67,172.6) .. controls (478.67,170.11) and (480.68,168.1) .. (483.17,168.1) .. controls (485.65,168.1) and (487.67,170.11) .. (487.67,172.6) .. controls (487.67,175.09) and (485.65,177.1) .. (483.17,177.1) .. controls (480.68,177.1) and (478.67,175.09) .. (478.67,172.6) -- cycle ;
%Shape: Circle [id:dp7005363351052425] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (491,154.1) .. controls (491,151.61) and (493.01,149.6) .. (495.5,149.6) .. controls (497.99,149.6) and (500,151.61) .. (500,154.1) .. controls (500,156.59) and (497.99,158.6) .. (495.5,158.6) .. controls (493.01,158.6) and (491,156.59) .. (491,154.1) -- cycle ;
%Shape: Circle [id:dp5131516311175763] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (491,191.1) .. controls (491,188.61) and (493.01,186.6) .. (495.5,186.6) .. controls (497.99,186.6) and (500,188.61) .. (500,191.1) .. controls (500,193.59) and (497.99,195.6) .. (495.5,195.6) .. controls (493.01,195.6) and (491,193.59) .. (491,191.1) -- cycle ;
%Shape: Circle [id:dp38829310474408074] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (503.4,172.6) .. controls (503.4,170.11) and (505.41,168.1) .. (507.9,168.1) .. controls (510.39,168.1) and (512.4,170.11) .. (512.4,172.6) .. controls (512.4,175.09) and (510.39,177.1) .. (507.9,177.1) .. controls (505.41,177.1) and (503.4,175.09) .. (503.4,172.6) -- cycle ;
%Shape: Circle [id:dp6003377245628321] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (524.7,172.5) .. controls (524.7,170.01) and (526.71,168) .. (529.2,168) .. controls (531.69,168) and (533.7,170.01) .. (533.7,172.5) .. controls (533.7,174.99) and (531.69,177) .. (529.2,177) .. controls (526.71,177) and (524.7,174.99) .. (524.7,172.5) -- cycle ;

    % Text Node
    \draw (379,111.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,141.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,172.09) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,241.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (283,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (322.5,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (363,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (420.1,194) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (382.4,194.52) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \ddots $};
    % Text Node
    \draw (292,45) node [anchor=north west][inner sep=0.75pt]   [align=left] {${Heat\ Zone}$};
    % Text Node
    \draw (492.00,150.41) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$p$}}};
    % Text Node
    \draw (479.75,168.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$q$}}};
    % Text Node
    \draw (492.45,188.12) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$r$}}};
    % Text Node
    \draw (525.00,166.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$q'$}}};
    % Text Node
    \draw (504.00,168.45) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$A$}}};

>>>>

%Shape: Ellipse [id:dp3980815479811872] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (493.14,156.7) .. controls (493.14,153.44) and (495.79,150.79) .. (499.05,150.79) .. controls (502.31,150.79) and (504.96,153.44) .. (504.96,156.7) .. controls (504.96,159.97) and (502.31,162.61) .. (499.05,162.61) .. controls (495.79,162.61) and (493.14,159.97) .. (493.14,156.7) -- cycle ;
%Shape: Ellipse [id:dp8208493476316323] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (493.14,205.29) .. controls (493.14,202.03) and (495.79,199.38) .. (499.05,199.38) .. controls (502.31,199.38) and (504.96,202.03) .. (504.96,205.29) .. controls (504.96,208.56) and (502.31,211.2) .. (499.05,211.2) .. controls (495.79,211.2) and (493.14,208.56) .. (493.14,205.29) -- cycle ;

@@

\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (476.94,181) .. controls (476.94,177.74) and (479.59,175.09) .. (482.85,175.09) .. controls (486.12,175.09) and (488.76,177.74) .. (488.76,181) .. controls (488.76,184.26) and (486.12,186.91) .. (482.85,186.91) .. controls (479.59,186.91) and (476.94,184.26) .. (476.94,181) -- cycle ;
%Shape: Ellipse [id:dp967421569400009] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (509.42,181) .. controls (509.42,177.74) and (512.07,175.09) .. (515.33,175.09) .. controls (518.6,175.09) and (521.24,177.74) .. (521.24,181) .. controls (521.24,184.26) and (518.6,186.91) .. (515.33,186.91) .. controls (512.07,186.91) and (509.42,184.26) .. (509.42,181) -- cycle ;
%Shape: Ellipse [id:dp938870324276512] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (537.4,180.87) .. controls (537.4,177.6) and (540.04,174.96) .. (543.31,174.96) .. controls (546.57,174.96) and (549.22,177.6) .. (549.22,180.87) .. controls (549.22,184.13) and (546.57,186.78) .. (543.31,186.78) .. controls (540.04,186.78) and (537.4,184.13) .. (537.4,180.87) -- cycle ;

@@

\draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (472.92,157.94) .. controls (472.92,149.47) and (479.78,142.6) .. (488.26,142.6) -- (537.95,142.6) .. controls (546.42,142.6) and (553.29,149.47) .. (553.29,157.94) -- (553.29,203.95) .. controls (553.29,212.43) and (546.42,219.29) .. (537.95,219.29) -- (488.26,219.29) .. controls (479.78,219.29) and (472.92,212.43) .. (472.92,203.95) -- cycle ;

@@

\draw    (493.14,156.7) -- (465.3,156.7) ;

@@

\draw    (476.94,180.82) -- (465.3,180.87) ;

@@

\draw    (493.14,205.29) -- (465.3,205.29) ;

@@

\draw    (482.85,181) -- (499.05,156.7) ;

@@

\draw    (482.85,181) -- (499.05,205.29) ;

@@

\draw    (499.05,156.7) -- (515.33,181) ;

@@

\draw    (499.05,205.29) -- (515.33,181) ;

@@

\draw    (482.85,181) -- (515.33,181) ;

@@

\draw    (499.05,205.29) -- (499.05,178.37) -- (499.05,156.7) ;

@@

\draw    (499.05,205.29) .. controls (516.94,205.22) and (533.75,202.59) .. (543.31,180.87) ;

@@

\draw    (499.05,156.7) .. controls (520.61,156.36) and (536.9,162.14) .. (543.31,180.87) ;

@@

\draw    (543.31,180.87) .. controls (523.77,163.72) and (499.6,165.82) .. (482.85,181) ;

@@

\draw    (543.31,180.87) .. controls (535.85,191.56) and (520.61,190.51) .. (515.33,181) ;

@@

\draw    (549.22,180.87) -- (559.85,180.87) ;
%Shape: Ellipse [id:dp28592847133985866] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (476.94,181) .. controls (476.94,177.74) and (479.59,175.09) .. (482.85,175.09) .. controls (486.12,175.09) and (488.76,177.74) .. (488.76,181) .. controls (488.76,184.26) and (486.12,186.91) .. (482.85,186.91) .. controls (479.59,186.91) and (476.94,184.26) .. (476.94,181) -- cycle ;
%Shape: Ellipse [id:dp7005363351052425] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (493.14,156.7) .. controls (493.14,153.44) and (495.79,150.79) .. (499.05,150.79) .. controls (502.31,150.79) and (504.96,153.44) .. (504.96,156.7) .. controls (504.96,159.97) and (502.31,162.61) .. (499.05,162.61) .. controls (495.79,162.61) and (493.14,159.97) .. (493.14,156.7) -- cycle ;
%Shape: Ellipse [id:dp5131516311175763] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (493.14,205.29) .. controls (493.14,202.03) and (495.79,199.38) .. (499.05,199.38) .. controls (502.31,199.38) and (504.96,202.03) .. (504.96,205.29) .. controls (504.96,208.56) and (502.31,211.2) .. (499.05,211.2) .. controls (495.79,211.2) and (493.14,208.56) .. (493.14,205.29) -- cycle ;
%Shape: Ellipse [id:dp38829310474408074] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (509.42,181) .. controls (509.42,177.74) and (512.07,175.09) .. (515.33,175.09) .. controls (518.6,175.09) and (521.24,177.74) .. (521.24,181) .. controls (521.24,184.26) and (518.6,186.91) .. (515.33,186.91) .. controls (512.07,186.91) and (509.42,184.26) .. (509.42,181) -- cycle ;
%Shape: Ellipse [id:dp6003377245628321] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (537.4,180.87) .. controls (537.4,177.6) and (540.04,174.96) .. (543.31,174.96) .. controls (546.57,174.96) and (549.22,177.6) .. (549.22,180.87) .. controls (549.22,184.13) and (546.57,186.78) .. (543.31,186.78) .. controls (540.04,186.78) and (537.4,184.13) .. (537.4,180.87) -- cycle ;
%Straight Lines [id:da025020526203919813] 
\draw    (305.63,73.33) -- (329.63,73.33) ;
\draw [shift={(331.63,73.33)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Shape: Brace [id:dp8023308836405996] 
\draw   (283.2,286.4) .. controls (283.2,291.07) and (285.53,293.4) .. (290.2,293.4) -- (314.2,293.4) .. controls (320.87,293.4) and (324.2,295.73) .. (324.2,300.4) .. controls (324.2,295.73) and (327.53,293.4) .. (334.2,293.4)(331.2,293.4) -- (358.2,293.4) .. controls (362.87,293.4) and (365.2,291.07) .. (365.2,286.4) ;

    % Text Node
    \draw (379,111.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,141.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,172.09) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,241.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (283,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (322.5,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (363,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (420.1,194) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (382.4,194.52) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \ddots $};
    % Text Node
    \draw (292,45) node [anchor=north west][inner sep=0.75pt]   [align=left] {${Heat\ Zone}$};
    % Text Node
    \draw (494.80,152.01) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$p$}}};
    % Text Node
    \draw (478.75,176.45) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$q$}}};
    % Text Node
    \draw (495.60,201.80) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$r$}}};
    % Text Node
    \draw (539.00,174.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$q'$}}};
    % Text Node
    \draw (510.60,175.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$A$}}};
